\documentclass{article}

% preambule
% needed package

% url need this
\usepackage[hidelinks=true]{hyperref}

% custom header footer layout settings
\usepackage{fancyhdr}
    \pagestyle{fancy}
    \rhead{}
    \lhead{}
    \rfoot{}
    \lfoot{}
    \cfoot{}
% remove horizontal line from fancyhdr
\renewcommand{\headrulewidth}{0pt}

% custom paper size
\usepackage[paperheight=233mm, paperwidth=178mm, top=1in,bottom=1in,right=1in,left=1in]{geometry}

\usepackage{color} % <= font color

% custom command <= creating bold horizontal rules
    \newcommand{\myline}
    {
        \begin{center}
            \(\star\ \star\ \star\ \star\ \star\ \star\ \star\ \star\)
        \end{center}
    }
    
    \newcommand{\HRule}{\rule{\linewidth}{2mm}}
    \newcommand{\garis}{\rule{\linewidth}{0.5mm}}
%%


\begin{document}

% bagian title start
\begin{titlepage}

\begin{flushright}
\textcolor{white}{hidden text}

\vspace{7cm}

\HRule \\[0.4cm]
{\large 2004 Ford F250 Super Duty Wiring Schematic }\\[0.4cm]
\HRule \\[1.5cm]

\large{File ID:}\\
\small{ 200-5ca96e95d2d }

\end{flushright}

\vfill

\begin{flushright}
\footnotesize{ For your convenience, we has placed some of the front \\
matter material after the index. Please use the Bookmarks \\
and Contents at a Glance links to access them. }
\end{flushright}

\end{titlepage}
% bagian title end
\noindent
{\textbf {\footnotesize 2004 Ford F250 Super Duty Wiring Schematic }}

\vspace{6pt}

\noindent
\scriptsize{Copyright @2014. All rights reserved. \\Printed in the United
  States of America.}

\noindent
\scriptsize{This books may be purchased for educational, business or
  sales promotional use. Online editions are also available for most
  titles. For more information, please contact our
  corporate/institutional sales department.}

\vfill

\noindent
\scriptsize{Many of the designations used by manufacture and sellers
  to distinguish their products are claimed as trademarks. Where those
  designations appear in this book, and we was aware of a trademark
  claim, the designations have been printed in caps or initial caps.}

\noindent
\scriptsize{While every precautions has been taken in the preparation of
  this book, the publisher and author assume no responsibility for
  errors or omissions, or for damage resulting from the use of the
  information contained herein.}

\clearpage

\noindent
\begin{center}
{\normalsize \emph{This page intentionally left blank}}
\end{center}

\clearpage

\section*{Preface}
{\normalsize
\begin{flushleft}
\emph{Congratulations!} You are now reading ``2004 ford f250 super duty wiring schematic''. The
purpose of this eBook is to educate and inform about 2004 ford f250 super duty wiring schematic.
\end{flushleft}

\begin{flushleft}
Ei ius mundi interpretaris. In saepe prodesset vel. Sit error legendos
iracundia te, option abhorreant sit ea. Corpora postulant forensibus
vis in, in vix possim pertinacia deterruisset. Per an latine detraxit
democritum, ex eam consul bonorum, at ullum deterruisset quo.
\end{flushleft}

\begin{flushleft}
Est et ignota labore, propriae adolescens voluptatum at eam. Mei
percipit neglegentur ut, pri in lorem partiendo. Malorum consectetuer
has ad, est dolorem fuisset at, vim ei hinc consulatu intellegam. Mel
eu saepe option phaedrum. Ne clita aliquam detraxit cum, eum enim
audiam concludaturque te, ex phaedrum dissentiunt mediocritatem mel.
\end{flushleft}

\begin{flushleft}
Ut augue putent melius eum, cu mel urbanitas voluptatibus. Sed ea
putant facilis definitiones, qui aliquam nominati eu, posse omnium
mentitum his at. Est no brute libris omittam. Audire explicari
vituperatoribus quo ei. Ad cum dolore nusquam sapientem, te cum
nonumes suavitate. Nam vide elitr consul no, primis explicari te qui.
\end{flushleft}
}


\vspace{20pt}

\noindent
{\color{blue}
\emph{
\large{
\underline{
\href{http://ads.ad-center.com/offer?prod=101&ref=4988911&q=2004 Ford F250 Super Duty Wiring Schematic }{Please register to continue reading}
}}}}


\end{document}